Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-04 thesis/paper.tex
added table and other changes

@@

\subsubsection{axparameter}

@@

These data seem to align with the comments made during the interview. For example, the interviewee expressed a desire to have features be added to the API more rapidly and more quickly than they have previously. This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable and citing their wish for more features and more frequent updates to the API.

@@

% 1 - Desire for new functionality
% 2 - Push for new functionality from partners
% 3 - Desire for a well designed API, interface improvements
% 4 - Desire to have a more maintainable API
%

%

>>>>

\begin{table}
       \centering
       \begin{tabular}[Ht]{|l|c|c|}
       \hline
       \textbf{Category} & \textbf{Prediction} & \textbf{Actual} \\
       \hline
       Updative & 15.4\% & 7.7\% \\
       \hline
       Groomative & 7.7\% & 0.0\% \\
       \hline
       Preventive & 7.7\% & 15.4\% \\
       \hline
       Enhancive & 53.8\% & 53.8\% \\
       \hline
       Reductive & 7.7\% & 7.7\% \\
       \hline
       Adaptive & 15.4\% & 7.7\% \\
       \hline
       \end{tabular}
       \caption{Category Distribution}
       \label{table:Categories}
\end{table}

@@

\subsubsection{ax\_parameter}

@@

These data seem to align with the comments made during the interview. For example, the interviewee expressed a desire to have features be added to the API more rapidly and more quickly than they have previously. This sentiment was also expressed to the interviewee by certain partners who suggested that the API was too stable, citing their wish for additional features and more frequent updates to the API.

@@

% 1 - Desire for new functionality 
% 2 - Push for new functionality from partners
% 3 - Desire for a well designed API, interface improvements
% 4 - Desire to have a maintainable API
% 5 - The majority of changes added to the API, rather than removed - Seems to support the paper which said most changes are refactorings?
%
